%                                                                 aa.dem
% AA vers. 9.1, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%

\documentclass{aa}  
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{natbib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\usepackage{xcolor}
\usepackage{blindtext}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \usepackage[options]{hyperref}
% To add links in your PDF file, use the package "hyperref"
% with options according to your LaTeX or PDFLaTeX drivers.
\usepackage{float}
%\usepackage{stfloats}
\usepackage{dblfloatfix}
\usepackage{afterpage}
\usepackage{ifthen}
\usepackage[morefloats=12]{morefloats}
\usepackage{placeins}
\usepackage{multicol}
%\usepackage[breaklinks,colorlinks,citecolor=blue]{hyperref}
\bibpunct{(}{)}{;}{a}{}{,}
\usepackage[switch]{lineno}
\definecolor{linkcolor}{rgb}{0.6,0,0}
\definecolor{citecolor}{rgb}{0,0,0.75}
\definecolor{urlcolor}{rgb}{0.12,0.46,0.7}
\usepackage[breaklinks, colorlinks, urlcolor=urlcolor,
    linkcolor=linkcolor,citecolor=citecolor,pdfencoding=auto]{hyperref}
\hypersetup{linktocpage}
\usepackage{bold-extra}

\usepackage[nameinlink,capitalise]{cleveref}
\crefname{section}{Sect.}{Sects.}
\crefname{table}{Table}{Tables}
\crefname{equation}{Eq.}{Eqs.}
\crefname{appendix}{Appendix}{Appendices}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\Crefname{equation}{Equation}{Equations}
\crefname{appendix}{Appendix}{Appendices}
\makeatletter
\AddToHook{cmd/appendix/before}{\def\cref@section@alias{appendix}}
\makeatother

\input{../../common/Planck}

% Custom definitions
\def\Cosmoglobe{\textsc{Cosmoglobe}}
\def\commanderthree{\texttt{Commander3}}
\def\commander{\texttt{Commander}}
\def\Planck{\textit{Planck}}
\def\WMAP{\textit{WMAP}}
\def\COBE{\textit{COBE}}
\def\GAIA{\textit{Gaia}}
\def\gaia{\textit{Gaia}}
\def\Gaia{\textit{Gaia}}
\def\WISE{WISE}
\def\AKARI{\textrm{{AKARI}}}
\def\IRAS{\textit{{IRAS}}}
\newcommand{\CII}{\ensuremath{\textsc{C\,ii}}}
\newcommand{\phm}{\phantom{-}}
\newcommand{\dv}[0]{\vec{d}}
\renewcommand{\t}[0]{\vec{t}}
\newcommand{\A}[0]{\tens{A}}
\newcommand{\B}[0]{\tens{B}}
\newcommand{\Y}[0]{\tens{Y}}
\newcommand{\G}[0]{\tens{G}}
\newcommand{\n}[0]{\vec{n}}
\newcommand{\red}[0]{\color{red}}
\newcommand{\green}[0]{\color{green}}
\newcommand{\s}[0]{\vec{s}}
\renewcommand{\a}[0]{\vec{a}}
\newcommand{\m}[0]{\vec{m}}
\newcommand{\bv}[0]{\vec{b}}
\newcommand{\f}[0]{\vec{f}}
\newcommand{\F}[0]{\tens{F}}
\newcommand{\T}[0]{\tens{T}}
\newcommand{\Cp}[0]{\tens{C}}
\renewcommand{\L}[0]{\tens{L}}
\newcommand{\g}[0]{\vec{g}}
\newcommand{\N}[0]{\tens{N}}
\newcommand{\M}[0]{\tens{M}}
\newcommand{\iN}[0]{\tens{N}^{-1}}
\newcommand{\iM}[0]{\tens{M}^{-1}}
\newcommand{\w}[0]{\vec{w}}
\renewcommand{\S}[0]{\tens{S}}
\renewcommand{\r}[0]{\vec{r}}
\renewcommand{\u}[0]{\vec{u}}
\newcommand{\q}[0]{\vec{q}}
\renewcommand{\v}[0]{\vec{v}}
\renewcommand{\P}[0]{\tens{P}}
\newcommand{\dt}[0]{d_t}
\newcommand{\di}[0]{d_i}
\newcommand{\nt}[0]{n_t}
\newcommand{\st}[0]{s_t}
\newcommand{\mt}[0]{m_t}
\newcommand{\ft}[0]{f_t}
\newcommand{\Te}[0]{T_{\rm e}}
\newcommand{\EM}[0]{\rm EM}
\newcommand{\mathsc}[1]{{\normalfont\textsc{#1}}}
\newcommand{\hi}{\ensuremath{\mathsc {H\,i}}}
\newcommand{\bpbold}{\bfseries{\scshape{BeyondPlanck}}}
\newcommand{\BP}{\textsc{BeyondPlanck}}
\newcommand{\bp}{\textsc{BeyondPlanck}}
\newcommand{\cosmoglobe}{\textsc{Cosmoglobe}}
%\newcommand{\Cosmoglobe}{\textsc{Cosmoglobe}}
\newcommand{\lfi}[0]{LFI}
\newcommand{\hfi}[0]{HFI}
\newcommand{\npipe}[0]{\texttt{NPIPE}}
\newcommand{\sroll}[0]{\texttt{SRoll}}
\newcommand{\K}[0]{\textit K}
\newcommand{\Ka}[0]{\textit{Ka}}
\newcommand{\Q}[0]{\textit Q}
\newcommand{\V}[0]{\textit V}
\newcommand{\W}[0]{\textit W}
\newcommand{\e}{\mathrm e}
\newcommand{\cvar}{\ensuremath{c(\vartheta, \varphi, \psi)}}


\def\Tcmb{\ifmmode T_\mathrm{CMB}\else $T_{\mathrm{CMB}}$\fi}
\def\Tcold{\ifmmode T_\mathrm{c}\else $T_{\mathrm{c}}$\fi}
\def\Text{\ifmmode T_\mathrm{e}\else $T_{\mathrm{e}}$\fi}
\def\Thot{\ifmmode T_\mathrm{h}\else $T_{\mathrm{h}}$\fi}
\def\Tnear{\ifmmode T_\mathrm{n}\else $T_{\mathrm{n}}$\fi}
\def\scmb{\ifmmode s_\mathrm{CMB}\else $s_{\mathrm{CMB}}$\fi}
\def\squad{\ifmmode s_\mathrm{quad}\else $s_{\mathrm{quad}}$\fi}
\def\ssynch{\ifmmode s_\mathrm{s}\else $s_\mathrm{s}$\fi}
\def\sdust{\ifmmode s_\mathrm{d}\else $s_{\mathrm{d}}$\fi}
\def\ssdust{\ifmmode s_\mathrm{sd}\else $s_{\mathrm{sd}}$\fi}
\def\same{\ifmmode s_\mathrm{AME}\else $s_{\mathrm{AME}}$\fi}
\def\ssrc{\ifmmode s_\mathrm{src}\else $s_{\mathrm{src}}$\fi}
\def\sco{\ifmmode s_\mathrm{CO}\else $s_{\mathrm{CO}}$\fi}
\def\sff{\ifmmode s_\mathrm{ff}\else $s_{\mathrm{ff}}$\fi}
\def\gff{\ifmmode g_\mathrm{ff}\else $g_{\mathrm{ff}}$\fi}
\def\fsynch{\ifmmode f_\mathrm{s}\else $f_{\mathrm{s}}$\fi}
\def\fsd{\ifmmode f_\mathrm{sd}\else $f_{\mathrm{sd}}$\fi}
\def\fame{\ifmmode f_\mathrm{AME}\else $f_{\mathrm{AME}}$\fi}
\def\alphasrc{\ifmmode \alpha_\mathrm{src}\else $\alpha_{\mathrm{src}}$\fi}
\def\bcold{\ifmmode \beta_\mathrm{c}\else $\beta_{\mathrm{c}}$\fi}
\def\bext{\ifmmode \beta_\mathrm{e}\else $\beta_{\mathrm{e}}$\fi}
\def\bhot{\ifmmode \beta_\mathrm{h}\else $\beta_{\mathrm{h}}$\fi}
\def\bnear{\ifmmode \beta_\mathrm{n}\else $\beta_{\mathrm{n}}$\fi}
\def\bsynch{\ifmmode \beta_\mathrm{s}\else $\beta_{\mathrm{s}}$\fi} 
\def\bsun{\ifmmode \beta_\mathrm{sun}\else $\beta_{\mathrm{sun}}$\fi} 
\def\nuzeros{\ifmmode \nu_{0,\mathrm{s}}\else $\nu_{0,\mathrm{s}}$\fi} 
\def\nuzeroff{\ifmmode \nu_{0,\mathrm{ff}}\else $\nu_{0,\mathrm{ff}}$\fi} 
\def\nuzerocold{\ifmmode \nu_{0,\mathrm{c}}\else $\nu_{0,\mathrm{c}}$\fi}
\def\nuzeroext{\ifmmode \nu_{0,\mathrm{e}}\else $\nu_{0,\mathrm{e}}$\fi}
\def\nuzerohot{\ifmmode \nu_{0,\mathrm{h}}\else $\nu_{0,\mathrm{h}}$\fi}
\def\nuzeronear{\ifmmode \nu_{0,\mathrm{n}}\else $\nu_{0,\mathrm{n}}$\fi} 
\def\nuzeroame{\ifmmode \nu_{0,\mathrm{AME}}\else $\nu_{0,\mathrm{AME}}$\fi} 
\def\nuzerosd{\ifmmode \nu_{0,\mathrm{}}\else $\nu_{0,\mathrm{sd}}$\fi} 
\def\nuzerosrc{\ifmmode \nu_{0,\mathrm{src}}\else $\nu_{0,\mathrm{src}}$\fi} 
\def\nup{\ifmmode \nu_{\mathrm{p}}\else $\nu_{\mathrm{p}}$\fi} 
\def\alphasd{\ifmmode \alpha_{\mathrm{sd}}\else $\alpha_{\mathrm{sd}}$\fi} 
\def\Te{\ifmmode T_{\mathrm{e}}\else $T_{\mathrm{e}}$\fi} 
\def\kB{\ifmmode k_\mathrm{B}\else $k_{\mathrm{B}}$\fi} 
\def\nside{\ifmmode N_{\mathrm{side}}\else $N_{\mathrm{side}}$\fi}

\begin{document} 

   \title{\bfseries{\Cosmoglobe\ DR3. High resolution thermal dust maps from the joint analysis of Planck HFI and AKARI}}

   \input{authors.tex}

   \titlerunning{\Cosmoglobe: AKARI reanalysis}
   \authorrunning{R.M.~Sullivan et al.}

   \date{\today} 
   
   \abstract{We present new high resolution thermal dust maps from the Cosmoglobe DR3 analysis of AKARI. In addition to the AKARI data we use the \Planck\ HFI, DIRBE, and FIRAS maps to better constrain the lower-frequency regime and set absolute calibration levels. This works build off of the Cosmoglobe DR2 and includes a new high resolution hot dust component, at \nside\ 8192 (with a beam full-width at half maximum of 3.5\arcmin), as well as the cold dust at \nside\ 4096(?), nearby dust and H$alpha$ dust correction components build off of template maps at \nside\ 2048. The new dust model is more physically motivated, with a modified blackbody spectrum at frequencies up to 900\,GHz, transitioning to a spline regime, until finally joining an astrodust motivated model for the highest frequencies. Thus, these new maps span the widest range of frequencies and allow for the inclusion of polycyclic aromatic hydrocarbons (PAH) as expected in the highest AKARI and DIRBE bands. These dust models can be used for better modeling of the dust distributions within the Milky Way galaxy, and will be imperative for future CMB studies, such as by LiteBIRD and Simons Observatory, to ensure the dust contamination is under control for future measures of CMB $B$-modes.}

   \keywords{ISM: general - Zodiacal dust, Interplanetary medium - Cosmology: observations, diffuse radiation - Galaxy: general}
   \maketitle
\setcounter{tocdepth}{2}
\tableofcontents
   
\section{Introduction}
Things to do:
% - write abstract\newline
% - 


Here things are introduced \citep{planck2016-l01}.

Tie into the other papers, relate back to DIRBE analysis results

Why is dust interesting, what does AKARI bring to the table with HFI

SED dust paper from Ana, CIB paper from Katrine, CII paper from Nils, tSZ paper?

In \cref{sec:data} we present the data used for this analysis, in particular the AKARI and Planck HFI data, as well as ancillary data sets, and the masks used for the analysis. In \cref{sec:method} we present our methodology for the analysis, the sky and data model and the Gibbs sampling approach. 
In \cref{sec:dust} we present our new high resolution dust maps and model, and several relevant summary statistics. Finally, in \cref{sec:conclusions} we provide our conclusion and in \cref{app:residuals} the residual maps from the analysis. All data sets and code bases can be found online at PROVIDE links. 

\section{Data}
\label{sec:data}
Figure with the summary bandpasses for each of the experiments? Or reference the SED later on maybe. 
\subsection{AKARI}
\label{sec:dat_akari}


\subsection{Planck HFI}
\label{sec:dat_planck}

\subsection{DIRBE?}

\subsection{Firas?}


\subsection{Ancillary data}
GAIA, WISE, HI4PI, H-alpha, CII, CO? 

\subsection{Masks}
\label{sec:masks}
Dust mask, chisq mask, AKARI mask, 


\section{Methodology}
\label{sec:method}

\subsection{Data model}
\label{sec:dat_model}
Comapre to planck hfi, big full maps and smaller cutouts of nice featrues
also power spectra, how to extend pysm to high resolution
show how it compared to pysm at the highest ell
contraints on spatial variations on the SED, frequency channerl diff maps


65 microns vs , can we put limits on the variations of the small scale SED
interesting for turbulence, small scale science, even at 5 arcmin and compare with hfi would be color

something to put limits on sed variations. 

masks, confidence regions, 

The maps are the main thing, show off the high resolution. 



\subsection{Sky model}
\label{sec:sky_model}

\subsection{Gibbs sampling}
\label{sec:gibbs}


\section{Dust model}
\label{sec:dust}
Hot dust, cold dust, nearby dust and hot dust correction (with H-alpha correlation?)
Reference Ana SED paper, maybe SED plot with akari band updates?

\subsection{Cold dust}
\label{sec:cold_dust}

\subsection{Hot dust}
\label{sec:hot_dust}

\subsection{Power-spectra}
\label{sec:ps}
Can we extend pysm to high ell, higher resolution dust features. High res spatial variations of SED. 


\subsection{Efficiency and difference maps}
\label{sec:efficiency}
Frequency channel differnce maps - spectral varaitions on small scales? Turbulence?


\subsection{AstroDust model, PAH? Comparison with pysm}
\label{sec:PAH}

\subsection{Correlations?}
\label{sec:corr}

\section{Conclusions}
\label{sec:conclusions}
Here things conclude.

\input{../common/acknowledgements}

\bibliographystyle{aa}
\bibliography{../../common/CG_bibliography,../../common/Planck_bib}%,references}

\clearpage
\appendix
\onecolumn
\section{Residuals}
\label{app:residuals}
Plots of the residuals

\section{Appendix 2}
\label{app:}

\end{document}
%%%% End of aa.dem
